---
title: "Running the CytokineProfile Shiny App Locally"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{R_installation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview

This guide shows how to install the **CytokineProfileShinyApp** package from GitHub and launch the Shiny app locally. Please make sure to have at least **R Version 4.3 or greater installed**.

The package now includes the app runtime, and the supported local-user launch path is `CytokineProfileShinyApp::run_app()`.

## 1. Install `pak`

Run the following line in the R console if `pak` is not already installed:

```{r, eval = FALSE}
if (!requireNamespace("pak", quietly = TRUE)) install.packages("pak")
```

## 2. Install the package from GitHub

Install the package directly from GitHub with:

```{r, eval = FALSE}
pak::pak("ZhangLabUKY/CytokineProfileShinyApp")
```

`pak` will resolve and install the package dependencies, including Bioconductor dependencies required by the app.

## 3. Launch the app

After installation, launch the app with:

```{r, eval = FALSE}
CytokineProfileShinyApp::run_app()
```

## 4. Optional note for developers using a local repository checkout

If you are developing from a checked-out copy of the repository, you can still run the app directly from the packaged launcher with:

```{r, eval = FALSE}
shiny::runApp("inst/app")
```

You can also open `inst/app/app.R` and click **Run App**. All Shiny code lives in `R/`, and the runtime launcher, config, and static assets live under `inst/app/`.

------------------------------------------------------------------------

*Last updated:* `r format(Sys.Date(), "%B %d, %Y")`
