---
title: "R_installation"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{R_installation}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## R Package Requirements

* base64enc
* shiny
* shinyjs
* dplyr
* ggplot2
* readxl
* bslib
* jsonlite
* fontawesome
* shinyWidgets
* shinyhelper
* DT
* shinyFeedback
* skimr
* shinycssloaders
* BiocManager
* mixOmics

Install the required packages using the following code:

```{r, echo=TRUE, warning = FALSE, message = FALSE, eval = FALSE}
install.packages(c(
  "base64enc",
  "shiny",
  "shinyjs",
  "dplyr",
  "ggplot2",
  "readxl",
  "bslib",
  "jsonlite",
  "fontawesome",
  "shinyWidgets",
  "shinyhelper",
  "DT",
  "shinyFeedback",
  "skimr",
  "shinycssloaders",
  "BiocManager"
))

# Install mixOmics from Bioconductor
BiocManager::install("mixOmics")
```

## Setup and Installation

1. Clone the repository from GitHub:
    Clone this repository or download the source code to your local machine.
2. Open RStudio:
    Open the project in RStudio or your preffered IDE. 
3. Install Dependencies: 
    Ensure all packages are installed. 
4. Run the Application:
   Launch the app by executing 
```{r, echo=TRUE, warning=FALSE, message=FALSE, eval=FALSE} 
shiny::runApp("app.R")
```
